\section{Discussion}
\label{sec:discussion}

\paragraph{Why the graph matters.}
The ablation in Section~\ref{sec:ablation} shows that a parameter-matched
GCN (86K params, same as GAT) outperforms a flat MLP (35K) by $2\times$
on 1-step prediction, ruling out parameter count as the explanation.
A service's latency depends primarily on the load arriving from its
direct callers, and message passing encodes this locality directly.
GAT's further advantage over GCN reflects the heterogeneity of call
weights---frontend routes 90\% of its traffic to product-catalog and
roughly 20\% to payment---which uniform aggregation dilutes.

\paragraph{Where the safety filter helps less.}
On bursty and flash-crowd traffic, NetDream-Safe still violates SLOs
more often than on steady traffic, because latency---the hardest
feature to predict (Appendix~\ref{app:perfeature})---is what drives
SLO breaches. Under distributional shift the constraint predictor's
in-distribution recall ($p=0.9984$) no longer applies, and the filter
provides best-effort rather than reliable rejection. Online model
adaptation on live cluster traces is the natural extension and we
leave it to future work.

\paragraph{Limitations.}
(1)~\emph{Statistical power.} EKS results use three seeds per cell;
the bootstrap 95\% CI on the aggregate violation advantage over
HPA-min3 crosses zero (Appendix~\ref{app:stats}), so the cost
advantage (tight CI, 54\%) is the primary empirical claim and the
violation advantage should be read as a same-tier result, not a
strict win.
(2)~\emph{Baseline coverage.} GraphPilot~\citep{chen2025graphpilot}
and KARMA~\citep{karma2025} were not publicly available at evaluation
time; we compare against their algorithmic paradigms via PPO-500K and
NetDream itself rather than head-to-head implementations. A
graph-structured PPO would be a stronger learned-policy ablation.
(3)~\emph{Topology scale.} Online Boutique's 11-service topology is
smaller than many production deployments; scaling to ${\sim}100$-node
graphs will require sparse or hierarchical attention rather than the
dense GAT used here.
(4)~\emph{Cost proxy.} Replica count proxies dollar cost; vCPU/memory
shapes and spot-vs-on-demand pricing are not modelled.
(5)~\emph{Service-call graph as a known input.} We assume the directed
service-call graph is known a priori, encoded once from the Online
Boutique application's deployment manifests. In production this graph
can be obtained automatically from a service mesh (e.g.\ Istio) or a
distributed-tracing system (e.g.\ Jaeger); dynamic topology changes
(services coming online or being deprecated) are out of scope.
